---
title: "Aggregating Results: Exercise"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    mathjax: local
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F)
```

```{r}
library(tidyverse)
```


# Data Preparation

# Exercise

- Load the dataset "txhousing", which holds information on Texas housing market.

```{r}
# code here
data("txhousing")
txhousing
```

```{r}
txhousing %>% head()
```

- Calculate the average sales for each city. During the calculation of mean values the result is coerced to NA, if there is a single NA present. Disable this functionality and change it so that missing values are excluded.

```{r}
# code here
y <- txhousing  %>%
  group_by(city) %>%
  summarise('Avg_sales'=mean(sales))
y


```


```{r}
z <- txhousing  %>%
  group_by(city) %>%
  summarise_at(vars(sales), list(name = mean))
z
```

```{r}
u <- txhousing  %>%
  group_by(city) %>%
  summarise(Mean = mean(sales, na.rm = T))
u
```

- Calculate the average sales for city and year and save it in object "tx_city_year".

```{r}
tx_city_year <- txhousing  %>%
  group_by(city,year) %>%
  summarise('mean_sales'=mean(sales, na.rm = T))

tx_city_year
```

Plot the data with ggplot:

```{r}
ggplot(tx_city_year, aes(x = year, y = mean_sales, col = city)) + 
   geom_line() + 
   labs(x = "Year", y = "Mean Sales", title = "Average Sales per Year and City")
```

